Inferring Invariants of Distributed Programs

### 2015-02-27 Doc/paper.tex
fixing compilation error and some typos

\usepackage{graphicx}
\usepackage[vlined,ruled]{algorithm2e}
\usepackage{xcolor}
\usepackage{listings}
\usepackage{hyperref}

\usepackage{lstlisting}

@@

\lstdefinelanguage{JavaScript}{
  keywords={typeof, new, true, false, catch, function, return, null, catch, switch, var, if, in, while, do, else, case, break},
  keywordstyle=\color{blue}\bfseries,
  ndkeywords={class, export, boolean, throw, implements, import},
  ndkeywordstyle=\color{darkgray}\bfseries,
  identifierstyle=\color{black},
  sensitive=false,
  commentstyle=\color{mygreen}\ttfamily,
  comment=[l]{//},
  morecomment=[s]{/*}{*/},
  stringstyle=\color{purple}\ttfamily,
  morestring=[b]',
  morestring=[b]"
}
\lstset{
  language=JavaScript,
  %backgroundcolor=\color{lightgray},
  extendedchars=true,
  basicstyle=\scriptsize\ttfamily,
  showstringspaces=false,
  showspaces=false,
  numbers=left,
  numberstyle=\tiny\color{mygray},
  numbersep=-6pt,
  tabsize=1,
  breaklines=true,
  showtabs=false,
  captionpos=b,
  numberblanklines=false,
  escapeinside=\[\]
}

@@

\begin{document}
%
% paper title
% can use linebreaks \\ within to get better formatting as desired
\title{Inferring Invariants in Distributed Programs}

@@

Yabandeh et al.\cite{yabandeh2011finding} proposed an approach to infer almost-invariants in distributed systems. They infer the invariants that are true in most cases and assume these invariants only get violated due to manifestation of bugs. There are a number of ways our approach differ from theirs: Their approach requires user to provide a list of variables and functions that they want to consider for inferring invariants while our approach infer these distributed state variables automatically. Moreover, they assume that an external module generates a trace of globally consistent state system for their algorithm while our approach extract these state through dynamic execution of the distributed system.

Ernst et al.\cite{ernst2001dynamically} infer invariants in a centralized program through executing the program on a collection of inputs and this invariant detector has been released as a tool called Daikon\cite{ernst2007daikon}. Although, we use their tool to infer invariants, detecting invariants in a distributed system poses unique challenges to identify distributed state and valid global states among a larger set of variables. Ne Win et al.\cite{NeWinEGKL04} use daikon to assist theorem provers for verifying distributed algorithms. To demonstrate their approach, they proved correctness of Paxos algorithm with their approach.

@@

In order to detect these variables, some form of dataflow analysis is required. This includes the dataflow of the distributed system as a whole and also in a single program. But currently there are no data flow analysis frameworks available for go programs.

@@

Our dynamic dataflow analysis is focused on mainly providing the following feature. Given a variable, start line and end line it will return a set of variables affected by that variable between start line and the end line.

>>>>

\usepackage{graphicx}
\usepackage[vlined,ruled]{algorithm2e}
\usepackage{xcolor}
\usepackage{listings}
\usepackage{listings-golang}
\usepackage{hyperref}

@@

\lstset{ % add your own preferences
    basicstyle=\footnotesize,
    keywordstyle=\color{red},
    numbers=left,
    numbersep=5pt,
    showstringspaces=false, 
    stringstyle=\color{blue},
    tabsize=4,
    language=Golang % this is it !
}

@@

\begin{document}
%
% paper title
% can use linebreaks \\ within to get better formatting as desired
\title{Inferring Invariants of Distributed Programs}

@@

Yabandeh et al.\cite{yabandeh2011finding} proposed an approach to infer almost-invariants in distributed systems. They infer the invariants that are true in most cases and assume these invariants only get violated due to manifestation of bugs. There are a number of ways our approach differ from theirs: Their approach requires user to provide a list of variables and functions that they want to consider for inferring invariants while our approach infers distributed state variables automatically. Moreover, they assume that an external module generates a trace of globally consistent state system for their algorithm while our approach extract these states through dynamic execution of the distributed system.

Ernst et al.\cite{ernst2001dynamically} infer invariants in a sequential program by executing the program on a collection of inputs. This invariant detector has been released as a tool called Daikon\cite{ernst2007daikon}. Although, we use their tool to infer invariants, detecting invariants in a distributed system poses unique challenges to identify distributed state and valid global states among a larger set of variables. Ne Win et al.\cite{NeWinEGKL04} use daikon to assist theorem provers for verifying distributed algorithms. To demonstrate their approach, they proved the correctness of the Paxos algorithm.

@@

To detect these variables, some form of dataflow analysis is required. This includes the dataflow of the distributed system as a whole and also in a single program. But currently there are no data flow analysis frameworks available for Go programs.

@@

Our dynamic dataflow analysis is focused on mainly providing the following features. Given a variable, start line and end line it will return a set of variables affected by that variable between start line and the end line.
